---
title: "SVM-HER2 tests"
output: html_document
---

#### genes: 'ERBB2', 'GRB7', 'MED1', 'FGFR1', 'STARD3'

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Required packages

```{r}
require(readr)
require(mlr)
require(VIM)
require(e1071)
require(ggplot2)
```

## Load HER2 Clinical data

```{r}
clinical_data <- as.data.frame(read_tsv("../data/her2_Clinical_Data.tsv"))

make.true.NA <- function(x) if(is.character(x)||is.factor(x)){
                                  is.na(x) <- x%in%c("[Not Available]","[Not Evaluated]"); x} else {
                                  x}
clinical_data <- as.data.frame(lapply(clinical_data, make.true.NA))

# aggr() shows how much is missing, and there is a lot missing
aggr(clinical_data[, 4:200 ])

row.names(clinical_data) <- clinical_data$X1

clinical_data$X1 <- NULL

clinical_data <- as.data.frame(t(clinical_data))

aggr(clinical_data)

pos_her2 <- gsub("\\.","-", rownames(clinical_data[which(clinical_data$her2_status_by_ihc == "Positive"),]))

neg_her2 <- gsub("\\.","-", rownames(clinical_data[which(clinical_data$her2_status_by_ihc == "Negative"),]))

brca_ids <- scan("../../cancerproject/proj_090817/tumor_IDs/tumorBRCA.txt", what = character(),
                 sep = "\t")
```

```{r}
write.table(file="../data/her2_positive_IDs.tsv", x=pos_her2, sep="\n", quote=F, row.names = F, col.names = F)
write.table(file="../data/her2_negative_IDs.tsv", x=neg_her2, sep="\n", quote=F, row.names = F, col.names = F)
```

## Load gene expression data

```{r}
#gene_expr_data <- as.data.frame(read_tsv("../../cancerproject/proj_090817/data/GSM1536837_06_01_15_TCGA_24.tumor_Rsubread_FeatureCounts.txt.gz"))

gene_expr_data <- as.data.frame(read_tsv("../data/her2_genes_TPM.txt"))

rownames(gene_expr_data) <- gene_expr_data$X1

gene_expr_data$X1 <- NULL

gene_expr_data <- as.data.frame(t(gene_expr_data))

gene_expr_data

ids <- rownames(gene_expr_data)

gene_expr_data <- as.data.frame(sapply(gene_expr_data, function(x){log2(x + 1)}))

rownames(gene_expr_data) <- ids

gene_expr_data

pos_her2_expr <- gene_expr_data[which(rownames(gene_expr_data) %in% pos_her2),]

pos_her2_expr$her2_status_by_ihc <- "Positive"

neg_her2_expr <- gene_expr_data[which(rownames(gene_expr_data) %in% neg_her2),]

neg_her2_expr$her2_status_by_ihc <- "Negative"

total_her2_expr <- rbind(pos_her2_expr, neg_her2_expr)

colnames(total_her2_expr) <- make.names(colnames(total_her2_expr))

training.her2_expression <- sample(seq_len(nrow(total_her2_expr)), nrow(total_her2_expr) / 2)

```

```{r}
training.ids <- c(sample(pos_her2, 150), sample(neg_her2, 150))

nrow(total_her2_expr[-which(row.names(total_her2_expr) %in% training.ids),])

as.numeric(total_her2_expr[training.ids, 'her2_status_by_ihc'] == "Positive")

plot(MED1 ~ GRB7, pch = ifelse(her2_status_by_ihc == "Positive", 16, 17), col = ifelse(her2_status_by_ihc == "Positive", "red", "green"), data = total_her2_expr[training.ids, ])
plot(STARD3 ~ GRB7, pch = ifelse(her2_status_by_ihc == "Positive", 16, 17), col = ifelse(her2_status_by_ihc == "Positive", "red", "green"), data = total_her2_expr[training.ids, ])
plot(MED1 ~ STARD3, pch = ifelse(her2_status_by_ihc == "Positive", 16, 17), col = ifelse(her2_status_by_ihc == "Positive", "red", "green"), data = total_her2_expr[training.ids, ])

pdf("../graphs/scatterplot_ERBB2vFGFR1.pdf", width = 8, height = 7)
plot(ERBB2 ~ FGFR1, pch = ifelse(her2_status_by_ihc == "Positive", 17, 16), col = ifelse(her2_status_by_ihc == "Positive", "green", "red"), data = total_her2_expr)
legend(9, 12.5, legend = c("Positive", "Negative"), col = c("green", "red"), pch = c(17, 16), title = "HER2 status")
title(main = "ERBB2 v. FGFR1 Log2 Expression")
dev.off()

pdf("../graphs/scatterplot_FGFR1vERBB2.pdf", width = 8, height = 7)
plot(FGFR1 ~ ERBB2, pch = ifelse(her2_status_by_ihc == "Positive", 17, 16), col = ifelse(her2_status_by_ihc == "Positive", "green", "red"), data = total_her2_expr)
legend(10.5, 10, legend = c("Positive", "Negative"), col = c("green", "red"), pch = c(17, 16), title = "HER2 status")
title(main = "ERBB2 v. FGFR1 Log2 Expression")
dev.off()
```

# Getting a protection stack overflow error, so I will try SVM in python

```{r}
write.table(total_her2_expr[training.ids,], file = "../data/training_her2.tsv", quote = F, sep = "\t")

write.table(total_her2_expr[-which(row.names(total_her2_expr) %in% training.ids),], file = "../data/testing_her2.tsv", quote = F, sep = "\t")
```

## Test 1: MED1 vs. STARD3

```{r}
#classif.svm <- makeLearner("classif.svm", predict.type = "prob")

#task_her2 <- makeClassifTask(data = total_her2_expr, target = "her2_status_by_ihc")

##IMPORTANT: create training set
#model_her2 <- train(classif.svm, task_her2, subset = training.her2_expression)
sink(file("../results/MED1_STARD3_noCV_results.txt", open = "w"), type = "output")
total_her2_expr$her2_status_by_ihc.numeric <- as.factor(total_her2_expr$her2_status_by_ihc == "Positive")

temp <- total_her2_expr[, -which(!(names(total_her2_expr) %in% c('MED1', 'STARD3', 'her2_status_by_ihc')))]

task <- makeClassifTask(data = temp, target = "her2_status_by_ihc")

svm.lrnr <- makeLearner("classif.svm", kernel = "linear", predict.type = "prob")

svm.model <- train(svm.lrnr, task, subset = which(row.names(temp) %in% training.ids))

svm.pred <- predict(svm.model, task = task, subset = which(!(row.names(temp) %in% training.ids)))

print("linear")
performance(svm.pred, measures = list(mmce, acc, auc))

plotLearnerPrediction(learner = makeLearner("classif.svm", kernel = "linear", predict.type = "prob"), task = task)


svm.lrnr <- makeLearner("classif.svm", kernel = "polynomial", predict.type = "prob")

svm.model <- train(svm.lrnr, task, subset = which(row.names(temp) %in% training.ids))

svm.pred <- predict(svm.model, task = task, subset = which(!(row.names(temp) %in% training.ids)))

print("polynomial")
performance(svm.pred, measures = list(mmce, acc, auc))

plotLearnerPrediction(learner = makeLearner("classif.svm", kernel = "polynomial", predict.type = "prob"), task = task)


svm.lrnr <- makeLearner("classif.svm", kernel = "radial", predict.type = "prob")

svm.model <- train(svm.lrnr, task, subset = which(row.names(temp) %in% training.ids))

svm.pred <- predict(svm.model, task = task, subset = which(!(row.names(temp) %in% training.ids)))

print("radial")
performance(svm.pred, measures = list(mmce, acc, auc))

plt.lrnr = plotLearnerPrediction(learner = makeLearner("classif.svm", kernel = "radial", predict.type = "prob"), task = task)

ggsave("../graphs/MED1vSTARD3.pdf", plot = plt.lrnr, device = "pdf")
sink(type = "output")
sink()

#svm.model <- svm(her2_status_by_ihc.numeric ~ ., data = total_her2_expr[training.ids, c('SOD2', 'FOS', 'ANXA1', 'BCL6', 'EGR1', 'her2_status_by_ihc.numeric') ], cost = 100, gamma = 1)
```

## Test 2: STARD3 vs GRB7

```{r}
sink(file("../results/GRB7_STARD3_noCV_results.txt", open = "w"), type = "output")

temp <- total_her2_expr[, -which(!(names(total_her2_expr) %in% c('GRB7', 'STARD3', 'her2_status_by_ihc')))]

task <- makeClassifTask(data = temp, target = "her2_status_by_ihc")

svm.lrnr <- makeLearner("classif.svm", kernel = "linear", predict.type = "prob")

svm.model <- train(svm.lrnr, task, subset = which(row.names(temp) %in% training.ids))

svm.pred <- predict(svm.model, task = task, subset = which(!(row.names(temp) %in% training.ids)))

print("linear")
performance(svm.pred, measures = list(mmce, acc, auc))

plotLearnerPrediction(learner = svm.lrnr, task = task)


svm.lrnr <- makeLearner("classif.svm", kernel = "polynomial", predict.type = "prob")

svm.model <- train(svm.lrnr, task, subset = which(row.names(temp) %in% training.ids))

svm.pred <- predict(svm.model, task = task, subset = which(!(row.names(temp) %in% training.ids)))

print("polynomial")
performance(svm.pred, measures = list(mmce, acc, auc))

plotLearnerPrediction(learner = svm.lrnr, task = task)


svm.lrnr <- makeLearner("classif.svm", kernel = "radial", predict.type = "prob")

svm.model <- train(svm.lrnr, task, subset = which(row.names(temp) %in% training.ids))

svm.pred <- predict(svm.model, task = task, subset = which(!(row.names(temp) %in% training.ids)))

print("radial")
performance(svm.pred, measures = list(mmce, acc, auc))

plt.lrnr = plotLearnerPrediction(learner = svm.lrnr, task = task)

ggsave("../graphs/GRB7vSTARD3.pdf", plot = plt.lrnr, device = "pdf")
sink(type = "output")
sink()
```

## Test 3: MED1 vs. GRB7

```{r}
sink(file("../results/GRB7_MED1_noCV_results.txt", open = "w"), type = "output")

temp <- total_her2_expr[, -which(!(names(total_her2_expr) %in% c('GRB7', 'MED1', 'her2_status_by_ihc')))]

task <- makeClassifTask(data = temp, target = "her2_status_by_ihc")

svm.lrnr <- makeLearner("classif.svm", kernel = "linear", predict.type = "prob")

svm.model <- train(svm.lrnr, task, subset = which(row.names(temp) %in% training.ids))

svm.pred <- predict(svm.model, task = task, subset = which(!(row.names(temp) %in% training.ids)))

print("linear")
performance(svm.pred, measures = list(mmce, acc, auc))

plotLearnerPrediction(learner = makeLearner("classif.svm", kernel = "linear", predict.type = "prob"), task = task)


svm.lrnr <- makeLearner("classif.svm", kernel = "polynomial", predict.type = "prob")

svm.model <- train(svm.lrnr, task, subset = which(row.names(temp) %in% training.ids))

svm.pred <- predict(svm.model, task = task, subset = which(!(row.names(temp) %in% training.ids)))

print("polynomial")
performance(svm.pred, measures = list(mmce, acc, auc))

plotLearnerPrediction(learner = makeLearner("classif.svm", kernel = "polynomial", predict.type = "prob"), task = task)


svm.lrnr <- makeLearner("classif.svm", kernel = "radial", predict.type = "prob")

svm.model <- train(svm.lrnr, task, subset = which(row.names(temp) %in% training.ids))

svm.pred <- predict(svm.model, task = task, subset = which(!(row.names(temp) %in% training.ids)))

print("radial")
performance(svm.pred, measures = list(mmce, acc, auc))

plt.lrnr = plotLearnerPrediction(learner = makeLearner("classif.svm", kernel = "radial", predict.type = "prob"), task = task)

ggsave("../graphs/GRB7vMED1.pdf", plot = plt.lrnr, device = "pdf")
sink(type = "output")
sink()
```

## Test 4: ERBB2 vs. FGFR1

```{r}
sink(file("../results/ERBB2_FGFR1_noCV_results.txt", open = "w"), type = "output")

temp <- total_her2_expr[, -which(!(names(total_her2_expr) %in% c('ERBB2', 'FGFR1', 'her2_status_by_ihc')))]

task <- makeClassifTask(data = temp, target = "her2_status_by_ihc")

svm.lrnr <- makeLearner("classif.svm", kernel = "linear", predict.type = "prob")

svm.model <- train(svm.lrnr, task, subset = which(row.names(temp) %in% training.ids))

svm.pred <- predict(svm.model, task = task, subset = which(!(row.names(temp) %in% training.ids)))

print("linear")
performance(svm.pred, measures = list(mmce, acc, auc))

plotLearnerPrediction(learner = makeLearner("classif.svm", kernel = "linear", predict.type = "prob"), task = task)


svm.lrnr <- makeLearner("classif.svm", kernel = "polynomial", predict.type = "prob")

svm.model <- train(svm.lrnr, task, subset = which(row.names(temp) %in% training.ids))

svm.pred <- predict(svm.model, task = task, subset = which(!(row.names(temp) %in% training.ids)))

print("polynomial")
performance(svm.pred, measures = list(mmce, acc, auc))

plotLearnerPrediction(learner = makeLearner("classif.svm", kernel = "polynomial", predict.type = "prob"), task = task)


svm.lrnr <- makeLearner("classif.svm", kernel = "radial", predict.type = "prob")

svm.model <- train(svm.lrnr, task, subset = which(row.names(temp) %in% training.ids))

svm.pred <- predict(svm.model, task = task, subset = which(!(row.names(temp) %in% training.ids)))

print("radial")
performance(svm.pred, measures = list(mmce, acc, auc))

plt.lrnr = plotLearnerPrediction(learner = makeLearner("classif.svm", kernel = "radial", predict.type = "prob"), task = task)

ggsave("../graphs/ERBB2vFGFR1.pdf", plot = plt.lrnr, device = "pdf")
sink(type = "output")
sink()
```

## Test 5: ERBB2 vs. MED1

```{r}
sink(file("../results/ERBB2_MED1_noCV_results.txt", open = "w"), type = "output")

temp <- total_her2_expr[, -which(!(names(total_her2_expr) %in% c('ERBB2', 'MED1', 'her2_status_by_ihc')))]

task <- makeClassifTask(data = temp, target = "her2_status_by_ihc")

svm.lrnr <- makeLearner("classif.svm", kernel = "linear", predict.type = "prob")

svm.model <- train(svm.lrnr, task, subset = which(row.names(temp) %in% training.ids))

svm.pred <- predict(svm.model, task = task, subset = which(!(row.names(temp) %in% training.ids)))

print("linear")
performance(svm.pred, measures = list(mmce, acc, auc))

plotLearnerPrediction(learner = makeLearner("classif.svm", kernel = "linear", predict.type = "prob"), task = task)


svm.lrnr <- makeLearner("classif.svm", kernel = "polynomial", predict.type = "prob")

svm.model <- train(svm.lrnr, task, subset = which(row.names(temp) %in% training.ids))

svm.pred <- predict(svm.model, task = task, subset = which(!(row.names(temp) %in% training.ids)))

print("polynomial")
performance(svm.pred, measures = list(mmce, acc, auc))

plotLearnerPrediction(learner = makeLearner("classif.svm", kernel = "polynomial", predict.type = "prob"), task = task)


svm.lrnr <- makeLearner("classif.svm", kernel = "radial", predict.type = "prob")

svm.model <- train(svm.lrnr, task, subset = which(row.names(temp) %in% training.ids))

svm.pred <- predict(svm.model, task = task, subset = which(!(row.names(temp) %in% training.ids)))

print("radial")
performance(svm.pred, measures = list(mmce, acc, auc))

plt.lrnr = plotLearnerPrediction(learner = makeLearner("classif.svm", kernel = "radial", predict.type = "prob"), task = task)

ggsave("../graphs/ERBB2vMED1.pdf", plot = plt.lrnr, device = "pdf")
sink(type = "output")
sink()
```

## Test 6: ERBB2 vs. GRB7

```{r}
sink(file("../results/ERBB2_GRB7_noCV_results.txt", open = "w"), type = "output")

temp <- total_her2_expr[, -which(!(names(total_her2_expr) %in% c('ERBB2', 'GRB7', 'her2_status_by_ihc')))]

task <- makeClassifTask(data = temp, target = "her2_status_by_ihc")

svm.lrnr <- makeLearner("classif.svm", kernel = "linear", predict.type = "prob")

svm.model <- train(svm.lrnr, task, subset = which(row.names(temp) %in% training.ids))

svm.pred <- predict(svm.model, task = task, subset = which(!(row.names(temp) %in% training.ids)))

print("linear")
performance(svm.pred, measures = list(mmce, acc, auc))

plotLearnerPrediction(learner = makeLearner("classif.svm", kernel = "linear", predict.type = "prob"), task = task)


svm.lrnr <- makeLearner("classif.svm", kernel = "polynomial", predict.type = "prob")

svm.model <- train(svm.lrnr, task, subset = which(row.names(temp) %in% training.ids))

svm.pred <- predict(svm.model, task = task, subset = which(!(row.names(temp) %in% training.ids)))

print("polynomial")
performance(svm.pred, measures = list(mmce, acc, auc))

plotLearnerPrediction(learner = makeLearner("classif.svm", kernel = "polynomial", predict.type = "prob"), task = task)


svm.lrnr <- makeLearner("classif.svm", kernel = "radial", predict.type = "prob")

svm.model <- train(svm.lrnr, task, subset = which(row.names(temp) %in% training.ids))

svm.pred <- predict(svm.model, task = task, subset = which(!(row.names(temp) %in% training.ids)))

print("radial")
performance(svm.pred, measures = list(mmce, acc, auc))

plt.lrnr = plotLearnerPrediction(learner = makeLearner("classif.svm", kernel = "radial", predict.type = "prob"), task = task)

ggsave("../graphs/ERBB2vGRB7.pdf", plot = plt.lrnr, device = "pdf")
sink(type = "output")
sink()
```

## Test 7: All

```{r}
sink(file("../results/All_noCV_results.txt", open = "w"), type = "output")

temp <- total_her2_expr[, -which(!(names(total_her2_expr) %in% c('ERBB2', 'GRB7', 'MED1', 'FGFR1', 'STARD3', 'her2_status_by_ihc')))]

task <- makeClassifTask(data = temp, target = "her2_status_by_ihc")

svm.lrnr <- makeLearner("classif.svm", kernel = "linear", predict.type = "prob")

svm.model <- train(svm.lrnr, task, subset = which(row.names(temp) %in% training.ids))

svm.pred <- predict(svm.model, task = task, subset = which(!(row.names(temp) %in% training.ids)))

print("linear")
performance(svm.pred, measures = list(mmce, acc, auc))

plotLearnerPrediction(learner = makeLearner("classif.svm", kernel = "linear", predict.type = "prob"), task = task)


svm.lrnr <- makeLearner("classif.svm", kernel = "polynomial", predict.type = "prob")

svm.model <- train(svm.lrnr, task, subset = which(row.names(temp) %in% training.ids))

svm.pred <- predict(svm.model, task = task, subset = which(!(row.names(temp) %in% training.ids)))

print("polynomial")
performance(svm.pred, measures = list(mmce, acc, auc))

plotLearnerPrediction(learner = makeLearner("classif.svm", kernel = "polynomial", predict.type = "prob"), task = task)


svm.lrnr <- makeLearner("classif.svm", kernel = "radial", predict.type = "prob")

svm.model <- train(svm.lrnr, task, subset = which(row.names(temp) %in% training.ids))

svm.pred <- predict(svm.model, task = task, subset = which(!(row.names(temp) %in% training.ids)))

print("radial")
performance(svm.pred, measures = list(mmce, acc, auc))

plt.lrnr = plotLearnerPrediction(learner = makeLearner("classif.svm", kernel = "radial", predict.type = "prob"), task = task)

ggsave("../graphs/all.pdf", plot = plt.lrnr, device = "pdf")
sink(type = "output")
sink()
```

## Calculate AUC using only ERBB2

```{r}
temp <- total_her2_expr[, -which(!(names(total_her2_expr) %in% c('ERBB2', 'her2_status_by_ihc')))]

task <- makeClassifTask(data = temp, target = "her2_status_by_ihc")

rdesc <- makeResampleDesc("CV", iters = 10L)

discrete_ps <- makeParamSet(
  makeDiscreteParam("cost", values = c(0.5, 1.0, 1.5, 2.0, 2.5, 3.0)),
  makeDiscreteParam("kernel", values = c("linear", "polynomial", "radial"))
)

ctrl <- makeTuneControlGrid()
res <- tuneParams(makeLearner("classif.svm", predict.type = "prob"), task = task, resampling = rdesc, par.set = discrete_ps, control = ctrl)


r <- resample(makeLearner("classif.svm", predict.type = "prob"), task, rdesc, measures = list(mmce, acc, auc))
sink(file("../results/only_ERB22_results.txt", open = "w"), type = "output")
print(r$aggr)
sink(type = "output")
sink()
```

## Same thing with ERBB2 and GRB7

```{r}
temp <- total_her2_expr[, -which(!(names(total_her2_expr) %in% c('ERBB2', 'GRB7', 'her2_status_by_ihc')))]

task <- makeClassifTask(data = temp, target = "her2_status_by_ihc")

rdesc <- makeResampleDesc("CV", iters = 10L)

discrete_ps <- makeParamSet(
  makeDiscreteParam("cost", values = c(0.5, 1.0, 1.5, 2.0, 2.5, 3.0)),
  makeDiscreteParam("kernel", values = c("linear", "polynomial", "radial"))
)

ctrl <- makeTuneControlGrid()
res <- tuneParams(makeLearner("classif.svm", predict.type = "prob"), task = task, resampling = rdesc, par.set = discrete_ps, control = ctrl)


r <- resample(makeLearner("classif.svm", predict.type = "prob"), task, rdesc, measures = list(mmce, acc, auc))
sink(file("../results/ERB22_GRB7_results.txt", open = "w"), type = "output")
print(r$aggr)
sink(type = "output")
sink()
```
## Same thing with all

```{r}
temp <- total_her2_expr[, -which(!(names(total_her2_expr) %in% c('ERBB2', 'GRB7', 'MED1', 'FGFR1', 'STARD3', 'her2_status_by_ihc')))]

task <- makeClassifTask(data = temp, target = "her2_status_by_ihc")

rdesc <- makeResampleDesc("CV", iters = 10L)

discrete_ps <- makeParamSet(
  makeDiscreteParam("cost", values = c(0.5, 1.0, 1.5, 2.0, 2.5, 3.0)),
  makeDiscreteParam("kernel", values = c("linear", "polynomial", "radial"))
)

ctrl <- makeTuneControlGrid()
res <- tuneParams(makeLearner("classif.svm", predict.type = "prob"), task = task, resampling = rdesc, par.set = discrete_ps, control = ctrl)


r <- resample(makeLearner("classif.svm", predict.type = "prob"), task, rdesc, measures = list(mmce, acc, auc))
sink(file("../results/All_results.txt", open = "w"), type = "output")
print(r$aggr)
sink(type = "output")
sink()
```

## Testing ksvm on the same thing

```{r}
discrete_ps = makeParamSet(
  makeDiscreteParam("C", values = c(0.5, 1.0, 1.5, 2.0)),
  makeDiscreteParam("sigma", values = c(0.5, 1.0, 1.5, 2.0))
)
ctrl = makeTuneControlGrid()
rdesc = makeResampleDesc("CV", iters = 3L)
res = tuneParams("classif.ksvm", task = task, resampling = rdesc,
  par.set = discrete_ps, control = ctrl)
```
# Ok, it's official, ksvm is not worth it

## Grab misclassified

```{r}
misclassied <- svm.pred$data[which(svm.pred$data$truth != svm.pred$data$response),]

misclassied.ids <-  row.names(misclassied)

misclassied.ids

misclassied.data <- total_her2_expr[which(row.names(total_her2_expr) %in% misclassied.ids),]

```

## RGB cube

```{r}
cubedraw <- function(res3d, min = 0, max = 255, cex = 2)
{
cube01 <- rbind(0,c(1,0,0),c(1,1,0),1,c(0,1,1),c(0,0,1),c(1,0,1),
c(1,0,0),c(1,0,1),1,c(1,1,0),
c(0,1,0),c(0,1,1), c(0,1,0),0)
cub <- min + (max-min)* cube01
res3d$points3d(cub[ 1:11,], cex = cex, type = 'b', lty = 1)
res3d$points3d(cub[11:15,], cex = cex, type = 'b', lty = 3)
}
```

## Compare different genes

```{r}
colors <- c("#E69F00", "#56B4E9")
colors <- colors[as.numeric(misclassied$truth)]

misclassied.data$truth <- misclassied$truth

for (i in 1:20){
  #print(names(misclassied.data)[c(i, i + 1, i + 2)])
  
  #s3d <- scatterplot3d(misclassied.data[,c(i, i + 1, i + 2)], pch = 16, color = colors, 
  #                     type = "h", box = T, angle = 55)
  
  mini.task = makeClassifTask(data = misclassied.data[,c(i, i +1, i + 2, ncol(misclassied.data))], target = "truth")
  print(plotLearnerPrediction(makeLearner("classif.svm", kernel = "radial"), task = mini.task, cv = 0))
}
```
